A Bayesian search to find \\high-mass black holes using LIGO data

### 2020-06-24 main.tex
Committed by TeXstudio

Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes. In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.  As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts \cite{gw190814}. These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.  Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6 \text{M}_\odot$. Thus, the existence of intermediate-mass black holes is still speculative.

If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network. According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at a rate of 0-10 yr\(^{-1}\) .  However, even after \citet{salemi2019search}'s
targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ?? High-mass mergers have
very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

@@

\hypertarget{methodology}{%
\chapter{Methodology}\label{methodology}}

This PhD project intends to provide new methods and insights to studying gravitational waves form high-mass systems.
Thus far, the project has focused on building up the infrastructure to compare the Bayesian Coherence Ratio of LIGO's
time-shifted \emph{background} triggers, \emph{foreground} triggers and \emph{software injections}. This chapter describes how we have
adapted the methods from \citet{bcr_paper} in our implementation.

@@

\begin{itemize}
\tightlist
\item
  \(\alpha = P(\mathcal{H}_S)/P(\mathcal{H}_I)\)
\item
  \(\beta = P(\mathcal{H}_{Gi}|\mathcal{H}_I)=1-P(\mathcal{H}_{N}|\mathcal{H}_I)\)
\end{itemize}

>>>>

Since the 1970s, there has been an accumulation of evidence for stellar-mass and supermassive black holes. In 2019, the Event Horizon Telescope provided the first visual evidence of the supermassive black hole M87  \cite{m87photo}.  As of January 2020, LIGO has confirmed ten binary black hole systems, and more than fifty public binary black hole alerts \cite{gw190814}. These various discoveries have firmly established the existence of stellar-mass black holes, supermassive black holes and binary black hole systems.  Interestingly, there is still no direct evidence for intermediate-mass black holes, the black holes that lie in between stellar-mass and supermassive black hole systems with masses between $10^2-10^6 \text{M}_\odot$. Thus, the existence of intermediate-mass black holes is still speculative. \\

If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network. According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at a rate of 0-10 yr\(^{-1}\) .  However, even after \citet{salemi2019search}'s
targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
far is approximately 80 M\({}_\odot\) \cite{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
due to their misclassification as short-duration instrumental noise transients \cite{blipGlitches}. As demonstrated in ?? High-mass mergers have
very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

@@

\section{Methodology}\label{methodology}
This PhD project intends to provide new methods and insights to studying gravitational waves form high-mass systems.
Thus far, the project has focused on building up the infrastructure to compare the Bayesian Coherence Ratio of LIGO's
time-shifted \emph{background} triggers, \emph{foreground} triggers and \emph{software injections}. This chapter describes how we have
adapted the methods from \citet{bcr_paper} in our implementation.

@@

\begin{itemize}
\item
  \(\alpha = P(\mathcal{H}_S)/P(\mathcal{H}_I)\)
\item
  \(\beta = P(\mathcal{H}_{Gi}|\mathcal{H}_I)=1-P(\mathcal{H}_{N}|\mathcal{H}_I)\)
\end{itemize}
